---
title: "Fundacion Juan March - Period Testing"
author: "Diego Enriquez"
date: "4/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE}
suppressMessages(library(data.table))
suppressMessages(library(lubridate))
suppressMessages(library(ggplot2))
suppressMessages(library(grid))

# Functions ==================================================================================================================================
source("fjm_func.R")
```


```{r echo=FALSE, warning=FALSE}
fjm_visitors <- readVisitorData()
fjm_visitors <- fjm_visitors[Date >= "2016-01-01"]
fjm_visitors[is.na(visitors)]$visitors = 0
```

```{r echo=FALSE, warning=FALSE}
ga_allws_nochn_all <- readQueryExplorerData("data/ga/fjm_allws_nochn_all.tsv", c("Date"))
ga_allws_nochn_os <- readQueryExplorerData("data/ga/fjm_allws_nochn_os.tsv", c("Date"))
ga_allws_nochn_es <- readQueryExplorerData("data/ga/fjm_allws_nochn_es.tsv", c("Date"))
ga_allws_nochn_do <- readQueryExplorerData("data/ga/fjm_allws_nochn_do.tsv", c("Date"))
ga_allws_nochn_lo <- readQueryExplorerData("data/ga/fjm_allws_nochn_lo.tsv", c("Date"))

ga_allws_chn_all <- readQueryExplorerData("data/ga/fjm_allws_chn_all.tsv", c("Date", "Channel"))
ga_allws_chn_os <- readQueryExplorerData("data/ga/fjm_allws_chn_os.tsv", c("Date", "Channel"))
ga_allws_chn_es <- readQueryExplorerData("data/ga/fjm_allws_chn_es.tsv", c("Date", "Channel"))
ga_allws_chn_do <- readQueryExplorerData("data/ga/fjm_allws_chn_do.tsv", c("Date", "Channel"))
ga_allws_chn_lo <- readQueryExplorerData("data/ga/fjm_allws_chn_lo.tsv", c("Date", "Channel"))

ga_arte_nochn_all <- readQueryExplorerData("data/ga/fjm_arte_nochn_all.tsv", c("Date"))
ga_arte_nochn_os <- readQueryExplorerData("data/ga/fjm_arte_nochn_os.tsv", c("Date"))
ga_arte_nochn_es <- readQueryExplorerData("data/ga/fjm_arte_nochn_es.tsv", c("Date"))
ga_arte_nochn_do <- readQueryExplorerData("data/ga/fjm_arte_nochn_do.tsv", c("Date"))
ga_arte_nochn_lo <- readQueryExplorerData("data/ga/fjm_arte_nochn_lo.tsv", c("Date"))

ga_arte_chn_all <- readQueryExplorerData("data/ga/fjm_arte_chn_all.tsv", c("Date", "Channel"))
ga_arte_chn_os <- readQueryExplorerData("data/ga/fjm_arte_chn_os.tsv", c("Date", "Channel"))
ga_arte_chn_es <- readQueryExplorerData("data/ga/fjm_arte_chn_es.tsv", c("Date", "Channel"))
ga_arte_chn_do <- readQueryExplorerData("data/ga/fjm_arte_chn_do.tsv", c("Date", "Channel"))
ga_arte_chn_lo <- readQueryExplorerData("data/ga/fjm_arte_chn_lo.tsv", c("Date", "Channel"))

ga_bibliotecas_nochn_all <- readQueryExplorerData("data/ga/fjm_bibliotecas_nochn_all.tsv", c("Date"))
ga_bibliotecas_nochn_os <- readQueryExplorerData("data/ga/fjm_bibliotecas_nochn_os.tsv", c("Date"))
ga_bibliotecas_nochn_es <- readQueryExplorerData("data/ga/fjm_bibliotecas_nochn_es.tsv", c("Date"))
ga_bibliotecas_nochn_do <- readQueryExplorerData("data/ga/fjm_bibliotecas_nochn_do.tsv", c("Date"))
ga_bibliotecas_nochn_lo <- readQueryExplorerData("data/ga/fjm_bibliotecas_nochn_lo.tsv", c("Date"))

ga_bibliotecas_chn_all <- readQueryExplorerData("data/ga/fjm_bibliotecas_chn_all.tsv", c("Date", "Channel"))
ga_bibliotecas_chn_os <- readQueryExplorerData("data/ga/fjm_bibliotecas_chn_os.tsv", c("Date", "Channel"))
ga_bibliotecas_chn_es <- readQueryExplorerData("data/ga/fjm_bibliotecas_chn_es.tsv", c("Date", "Channel"))
ga_bibliotecas_chn_do <- readQueryExplorerData("data/ga/fjm_bibliotecas_chn_do.tsv", c("Date", "Channel"))
ga_bibliotecas_chn_lo <- readQueryExplorerData("data/ga/fjm_bibliotecas_chn_lo.tsv", c("Date", "Channel"))

ga_conferencias_nochn_all <- readQueryExplorerData("data/ga/fjm_conferencias_nochn_all.tsv", c("Date"))
ga_conferencias_nochn_os <- readQueryExplorerData("data/ga/fjm_conferencias_nochn_os.tsv", c("Date"))
ga_conferencias_nochn_es <- readQueryExplorerData("data/ga/fjm_conferencias_nochn_es.tsv", c("Date"))
ga_conferencias_nochn_do <- readQueryExplorerData("data/ga/fjm_conferencias_nochn_do.tsv", c("Date"))
ga_conferencias_nochn_lo <- readQueryExplorerData("data/ga/fjm_conferencias_nochn_lo.tsv", c("Date"))

ga_conferencias_chn_all <- readQueryExplorerData("data/ga/fjm_conferencias_chn_all.tsv", c("Date", "Channel"))
ga_conferencias_chn_os <- readQueryExplorerData("data/ga/fjm_conferencias_chn_os.tsv", c("Date", "Channel"))
ga_conferencias_chn_es <- readQueryExplorerData("data/ga/fjm_conferencias_chn_es.tsv", c("Date", "Channel"))
ga_conferencias_chn_do <- readQueryExplorerData("data/ga/fjm_conferencias_chn_do.tsv", c("Date", "Channel"))
ga_conferencias_chn_lo <- readQueryExplorerData("data/ga/fjm_conferencias_chn_lo.tsv", c("Date", "Channel"))

ga_engws_nochn_all <- readQueryExplorerData("data/ga/fjm_engws_nochn_all.tsv", c("Date"))
ga_engws_nochn_os <- readQueryExplorerData("data/ga/fjm_engws_nochn_os.tsv", c("Date"))
ga_engws_nochn_es <- readQueryExplorerData("data/ga/fjm_engws_nochn_es.tsv", c("Date"))
ga_engws_nochn_do <- readQueryExplorerData("data/ga/fjm_engws_nochn_do.tsv", c("Date"))
ga_engws_nochn_lo <- readQueryExplorerData("data/ga/fjm_engws_nochn_lo.tsv", c("Date"))

ga_engws_chn_all <- readQueryExplorerData("data/ga/fjm_engws_chn_all.tsv", c("Date", "Channel"))
ga_engws_chn_os <- readQueryExplorerData("data/ga/fjm_engws_chn_os.tsv", c("Date", "Channel"))
ga_engws_chn_es <- readQueryExplorerData("data/ga/fjm_engws_chn_es.tsv", c("Date", "Channel"))
ga_engws_chn_do <- readQueryExplorerData("data/ga/fjm_engws_chn_do.tsv", c("Date", "Channel"))
ga_engws_chn_lo <- readQueryExplorerData("data/ga/fjm_engws_chn_lo.tsv", c("Date", "Channel"))

ga_musica_nochn_all <- readQueryExplorerData("data/ga/fjm_musica_nochn_all.tsv", c("Date"))
ga_musica_nochn_os <- readQueryExplorerData("data/ga/fjm_musica_nochn_os.tsv", c("Date"))
ga_musica_nochn_es <- readQueryExplorerData("data/ga/fjm_musica_nochn_es.tsv", c("Date"))
ga_musica_nochn_do <- readQueryExplorerData("data/ga/fjm_musica_nochn_do.tsv", c("Date"))
ga_musica_nochn_lo <- readQueryExplorerData("data/ga/fjm_musica_nochn_lo.tsv", c("Date"))

ga_musica_chn_all <- readQueryExplorerData("data/ga/fjm_musica_chn_all.tsv", c("Date", "Channel"))
ga_musica_chn_os <- readQueryExplorerData("data/ga/fjm_musica_chn_os.tsv", c("Date", "Channel"))
ga_musica_chn_es <- readQueryExplorerData("data/ga/fjm_musica_chn_es.tsv", c("Date", "Channel"))
ga_musica_chn_do <- readQueryExplorerData("data/ga/fjm_musica_chn_do.tsv", c("Date", "Channel"))
ga_musica_chn_lo <- readQueryExplorerData("data/ga/fjm_musica_chn_lo.tsv", c("Date", "Channel"))

daysinfo <- data.table(Date = seq(as.Date("2017-07-01"), as.Date("2018-07-12"), by = "day"))
daysinfo$weekNum <- wday(daysinfo$Date, week_start = 1)
daysinfo$isFirstSunday <- wday(daysinfo$Date, week_start = 1) == 7 & day(daysinfo$Date) <= 7

# teststart <- "2017-07-01"  # Values for Full Data
# testend <- "2018-07-12" 
# maxlag <- 31
# visitordata <- fleet_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]

# Common variables
maxlag <- 15
metric <- "Sessions"
metricidx <- 3
#  1 Users
#  2 UsersOld
#  3 Sessions
#  4 SessionsNew
#  5 SessionsOld
#  6 SessionsBounce
#  7 SessionsNoBounce
#  8 AvgSessionDuration
#  9 Pageviews
# 10 PageviewsSession
# 11 UniquePageviews
# 12 AvgTimeOnPage
```

# By Year

### 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-08-04"
testend <- "2016-12-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-01-01"
testend <- "2017-12-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-01-01"
testend <- "2018-06-24"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

# By Season

### Autumn 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-08-17"
testend <- "2016-11-30"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 8)
```

### Winter 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-11-16"
testend <- "2017-02-28"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### Spring 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-02-14"
testend <- "2017-05-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### Summer 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-05-17"
testend <- "2017-08-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 6)
```

### Autumn 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-08-17"
testend <- "2017-11-30"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 2)
```

### Winter 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-11-16"
testend <- "2018-02-28"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### Spring 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-02-14"
testend <- "2018-05-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### Summer 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-05-17"
testend <- "2018-06-24"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 7)
```




# By Holidays

Source: http://blog.activityhero.com/san-diego-unified-school-calendar/#sthash.n2hzZ9EV.dpbs

### Summer break 2016


### Christmas break 2016



### Easter break 2017



### Summer break 2017


### Christmas break 2017


### Easter break 2018



# By Month

### August 2016

Visitor data has no data
```{r echo=FALSE, fig.width=10}
# teststart <- "2016-08-19"
# testend <- "2016-08-31"
# 
# visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
# gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
# # getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions
# # 
# plotLagComparisonv2(trendValues(gamericdata),
#                     trendValues(visitordata),
#                     plotstart = teststart,
#                     plotend = testend,
#                     metric = metric,
#                     dlag = 0)
```

### September 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-08-17"
testend <- "2016-09-30"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 8)
```

### October 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-09-16"
testend <- "2016-10-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 3)
```

### November 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-10-17"
testend <- "2016-11-30"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 11)
```

### December 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-11-16"
testend <- "2016-12-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### January 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2016-12-17"
testend <- "2017-01-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 4)
```

### February 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-01-17"
testend <- "2017-02-28"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### March 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-02-14"
testend <- "2017-03-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 9)
```

### April 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-03-17"
testend <- "2017-04-30"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### May 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-04-16"
testend <- "2017-05-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 15)
```

### Jun 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-05-17"
testend <- "2017-06-30"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 5)
```


### July 2017

Visitor data has no data
```{r echo=FALSE, fig.width=10}
teststart <- "2017-06-16"
testend <- "2017-07-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
# getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions
# 
plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### August 2017

Visitor data has no data
```{r echo=FALSE, fig.width=10}
teststart <- "2017-07-17"
testend <- "2017-08-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
# getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions
# 
plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### September 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-08-17"
testend <- "2017-09-30"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 3)
```

### October 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-09-16"
testend <- "2017-10-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 2)
```

### November 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-10-17"
testend <- "2017-11-30"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### December 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-11-16"
testend <- "2017-12-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### January 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2017-12-17"
testend <- "2018-01-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### February 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-01-17"
testend <- "2018-02-28"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### March 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-02-14"
testend <- "2018-03-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### April 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-03-17"
testend <- "2018-04-30"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 9)
```

### May 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-04-16"
testend <- "2018-05-31"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 15)
```

### June 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-05-17"
testend <- "2018-06-24"

visitordata <- fjm_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(trendValues(gamericdata), trendValues(visitordata), maxlag = maxlag))[metricidx,]  # 3 Sessions

plotLagComparisonv2(trendValues(gamericdata),
                    trendValues(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 7)
```

