---
title: "Fundacion Juan March - Bet Correlations"
author: "Diego Enriquez"
date: "4/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE}
suppressMessages(library(data.table))
suppressMessages(library(lubridate))
suppressMessages(library(ggplot2))
suppressMessages(library(grid))

# Functions ==================================================================================================================================
source("fjm_func.R")
```


```{r echo=FALSE, warning=FALSE}
fjm_visitors <- readVisitorData()
fjm_visitors <- fjm_visitors[Date >= "2016-01-01"]
fjm_visitors[is.na(visitors)]$visitors = 0
```

```{r echo=FALSE, warning=FALSE}
ga_allws_nochn_all <- readQueryExplorerData("data/ga/fjm_allws_nochn_all.tsv", c("Date"))
ga_allws_nochn_os <- readQueryExplorerData("data/ga/fjm_allws_nochn_os.tsv", c("Date"))
ga_allws_nochn_es <- readQueryExplorerData("data/ga/fjm_allws_nochn_es.tsv", c("Date"))
ga_allws_nochn_do <- readQueryExplorerData("data/ga/fjm_allws_nochn_do.tsv", c("Date"))
ga_allws_nochn_lo <- readQueryExplorerData("data/ga/fjm_allws_nochn_lo.tsv", c("Date"))

ga_allws_chn_all <- readQueryExplorerData("data/ga/fjm_allws_chn_all.tsv", c("Date", "Channel"))
ga_allws_chn_os <- readQueryExplorerData("data/ga/fjm_allws_chn_os.tsv", c("Date", "Channel"))
ga_allws_chn_es <- readQueryExplorerData("data/ga/fjm_allws_chn_es.tsv", c("Date", "Channel"))
ga_allws_chn_do <- readQueryExplorerData("data/ga/fjm_allws_chn_do.tsv", c("Date", "Channel"))
ga_allws_chn_lo <- readQueryExplorerData("data/ga/fjm_allws_chn_lo.tsv", c("Date", "Channel"))

ga_arte_nochn_all <- readQueryExplorerData("data/ga/fjm_arte_nochn_all.tsv", c("Date"))
ga_arte_nochn_os <- readQueryExplorerData("data/ga/fjm_arte_nochn_os.tsv", c("Date"))
ga_arte_nochn_es <- readQueryExplorerData("data/ga/fjm_arte_nochn_es.tsv", c("Date"))
ga_arte_nochn_do <- readQueryExplorerData("data/ga/fjm_arte_nochn_do.tsv", c("Date"))
ga_arte_nochn_lo <- readQueryExplorerData("data/ga/fjm_arte_nochn_lo.tsv", c("Date"))

ga_arte_chn_all <- readQueryExplorerData("data/ga/fjm_arte_chn_all.tsv", c("Date", "Channel"))
ga_arte_chn_os <- readQueryExplorerData("data/ga/fjm_arte_chn_os.tsv", c("Date", "Channel"))
ga_arte_chn_es <- readQueryExplorerData("data/ga/fjm_arte_chn_es.tsv", c("Date", "Channel"))
ga_arte_chn_do <- readQueryExplorerData("data/ga/fjm_arte_chn_do.tsv", c("Date", "Channel"))
ga_arte_chn_lo <- readQueryExplorerData("data/ga/fjm_arte_chn_lo.tsv", c("Date", "Channel"))

ga_bibliotecas_nochn_all <- readQueryExplorerData("data/ga/fjm_bibliotecas_nochn_all.tsv", c("Date"))
ga_bibliotecas_nochn_os <- readQueryExplorerData("data/ga/fjm_bibliotecas_nochn_os.tsv", c("Date"))
ga_bibliotecas_nochn_es <- readQueryExplorerData("data/ga/fjm_bibliotecas_nochn_es.tsv", c("Date"))
ga_bibliotecas_nochn_do <- readQueryExplorerData("data/ga/fjm_bibliotecas_nochn_do.tsv", c("Date"))
ga_bibliotecas_nochn_lo <- readQueryExplorerData("data/ga/fjm_bibliotecas_nochn_lo.tsv", c("Date"))

ga_bibliotecas_chn_all <- readQueryExplorerData("data/ga/fjm_bibliotecas_chn_all.tsv", c("Date", "Channel"))
ga_bibliotecas_chn_os <- readQueryExplorerData("data/ga/fjm_bibliotecas_chn_os.tsv", c("Date", "Channel"))
ga_bibliotecas_chn_es <- readQueryExplorerData("data/ga/fjm_bibliotecas_chn_es.tsv", c("Date", "Channel"))
ga_bibliotecas_chn_do <- readQueryExplorerData("data/ga/fjm_bibliotecas_chn_do.tsv", c("Date", "Channel"))
ga_bibliotecas_chn_lo <- readQueryExplorerData("data/ga/fjm_bibliotecas_chn_lo.tsv", c("Date", "Channel"))

ga_conferencias_nochn_all <- readQueryExplorerData("data/ga/fjm_conferencias_nochn_all.tsv", c("Date"))
ga_conferencias_nochn_os <- readQueryExplorerData("data/ga/fjm_conferencias_nochn_os.tsv", c("Date"))
ga_conferencias_nochn_es <- readQueryExplorerData("data/ga/fjm_conferencias_nochn_es.tsv", c("Date"))
ga_conferencias_nochn_do <- readQueryExplorerData("data/ga/fjm_conferencias_nochn_do.tsv", c("Date"))
ga_conferencias_nochn_lo <- readQueryExplorerData("data/ga/fjm_conferencias_nochn_lo.tsv", c("Date"))

ga_conferencias_chn_all <- readQueryExplorerData("data/ga/fjm_conferencias_chn_all.tsv", c("Date", "Channel"))
ga_conferencias_chn_os <- readQueryExplorerData("data/ga/fjm_conferencias_chn_os.tsv", c("Date", "Channel"))
ga_conferencias_chn_es <- readQueryExplorerData("data/ga/fjm_conferencias_chn_es.tsv", c("Date", "Channel"))
ga_conferencias_chn_do <- readQueryExplorerData("data/ga/fjm_conferencias_chn_do.tsv", c("Date", "Channel"))
ga_conferencias_chn_lo <- readQueryExplorerData("data/ga/fjm_conferencias_chn_lo.tsv", c("Date", "Channel"))

ga_engws_nochn_all <- readQueryExplorerData("data/ga/fjm_engws_nochn_all.tsv", c("Date"))
ga_engws_nochn_os <- readQueryExplorerData("data/ga/fjm_engws_nochn_os.tsv", c("Date"))
ga_engws_nochn_es <- readQueryExplorerData("data/ga/fjm_engws_nochn_es.tsv", c("Date"))
ga_engws_nochn_do <- readQueryExplorerData("data/ga/fjm_engws_nochn_do.tsv", c("Date"))
ga_engws_nochn_lo <- readQueryExplorerData("data/ga/fjm_engws_nochn_lo.tsv", c("Date"))

ga_engws_chn_all <- readQueryExplorerData("data/ga/fjm_engws_chn_all.tsv", c("Date", "Channel"))
ga_engws_chn_os <- readQueryExplorerData("data/ga/fjm_engws_chn_os.tsv", c("Date", "Channel"))
ga_engws_chn_es <- readQueryExplorerData("data/ga/fjm_engws_chn_es.tsv", c("Date", "Channel"))
ga_engws_chn_do <- readQueryExplorerData("data/ga/fjm_engws_chn_do.tsv", c("Date", "Channel"))
ga_engws_chn_lo <- readQueryExplorerData("data/ga/fjm_engws_chn_lo.tsv", c("Date", "Channel"))

ga_musica_nochn_all <- readQueryExplorerData("data/ga/fjm_musica_nochn_all.tsv", c("Date"))
ga_musica_nochn_os <- readQueryExplorerData("data/ga/fjm_musica_nochn_os.tsv", c("Date"))
ga_musica_nochn_es <- readQueryExplorerData("data/ga/fjm_musica_nochn_es.tsv", c("Date"))
ga_musica_nochn_do <- readQueryExplorerData("data/ga/fjm_musica_nochn_do.tsv", c("Date"))
ga_musica_nochn_lo <- readQueryExplorerData("data/ga/fjm_musica_nochn_lo.tsv", c("Date"))

ga_musica_chn_all <- readQueryExplorerData("data/ga/fjm_musica_chn_all.tsv", c("Date", "Channel"))
ga_musica_chn_os <- readQueryExplorerData("data/ga/fjm_musica_chn_os.tsv", c("Date", "Channel"))
ga_musica_chn_es <- readQueryExplorerData("data/ga/fjm_musica_chn_es.tsv", c("Date", "Channel"))
ga_musica_chn_do <- readQueryExplorerData("data/ga/fjm_musica_chn_do.tsv", c("Date", "Channel"))
ga_musica_chn_lo <- readQueryExplorerData("data/ga/fjm_musica_chn_lo.tsv", c("Date", "Channel"))

daysinfo <- data.table(Date = seq(as.Date("2016-01-01"), as.Date("2018-06-24"), by = "day"))
daysinfo$weekNum <- wday(daysinfo$Date, week_start = 1)
daysinfo$monthNum <- mday(daysinfo$Date)
daysinfo$isFirstSunday <- wday(daysinfo$Date, week_start = 1) == 7 & day(daysinfo$Date) <= 7

# teststart <- "2017-07-01"  # Values for Full Data
# testend <- "2018-07-12" 
maxlag <- 31
# visitordata <- fleet_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
```

# Art

#### Locals, Organic Search, Sessions, corr: 0.905

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_arte_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "Sessions"
dlag <- 0
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```





#### Without moving average

```{r echo=FALSE, fig.width=10, warning=FALSE}
# teststart <- "2017-07-01"  # Values for Full Data
# testend <- "2018-07-12" 
# maxlag <- 31
# visitordata <- fleet_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
# plotLagComparison(ga_admin_nochn_all[Date >= teststart & Date <= testend],
#                     visitordata,
#                     metric = "SessionsNew",
#                     dlag = 0)
```

#### Spain, Organic Search, SessionsNew, corr: 0.904

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_arte_chn_es[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "Sessions"
dlag <- 0
plotLagComparison(movingAverage(gadata),
                  movingAverage(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(movingAverage(gadata),
                           movingAverage(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### All locations, all channels, SessionsOld, corr: 0.873

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-01-01"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_arte_nochn_all[Date >= teststart & Date <= testend]
metric <- "SessionsOld"
dlag <- 0
plotLagComparison(movingAverage(gadata),
                  movingAverage(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(movingAverage(gadata),
                           movingAverage(visitordata),
                           metric = metric,
                           dlag = dlag)
```

# All Website

#### Locals, Organic Search, SessionsBounce, corr: 0.876

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_allws_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "SessionsBounce"
dlag <- 0
plotLagComparison(movingAverage(gadata),
                  movingAverage(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(movingAverage(gadata),
                           movingAverage(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### Spain, Organic Search, Sessions, corr: 0.808

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_allws_chn_es[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "Sessions"
dlag <- 0
plotLagComparison(movingAverage(gadata),
                  movingAverage(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(movingAverage(gadata),
                           movingAverage(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### Spain, Direct, SessionsOld, corr: 0.802

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_allws_chn_es[Channel == "Direct" & Date >= teststart & Date <= testend]
metric <- "SessionsOld"
dlag <- 0
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

# Lectures

#### Spain, Organic Search, SessionsOld, corr: 0.751

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_conferencias_chn_es[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "SessionsOld"
dlag <- 0
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### Domestic, Organic Search, SessionsNoBounce, corr: 0.727

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_conferencias_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "SessionsNoBounce"
dlag <- 0
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### Spain, Direct, UsersOld, corr: 0.723

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_conferencias_chn_es[Channel == "Direct" & Date >= teststart & Date <= testend]
metric <- "UsersOld"
dlag <- 0
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

# English Website

#### All locations, All channels, SessionsBounce, corr: 0.704

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-01-01"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_engws_nochn_all[Date >= teststart & Date <= testend]
metric <- "SessionsBounce"
dlag <- 0
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### All locations, Organic Search, SessionsBounce, corr: 0.691

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-01-01"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_engws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "SessionsBounce"
dlag <- 0
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### Locals, All channels, SessionsBounce, corr: 0.551

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_engws_nochn_lo[Date >= teststart & Date <= testend]
metric <- "SessionsBounce"
dlag <- 16
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

# Music

#### Locals, Organic Search, Users, corr: 0.703

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_musica_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "Users"
dlag <- 1
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### Spain, Organic Search, UsersOld, corr: 0.694

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_musica_chn_es[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "UsersOld"
dlag <- 1
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### Locals, Direct, UsersOld, corr: 0.688

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_musica_chn_lo[Channel == "Direct" & Date >= teststart & Date <= testend]
metric <- "UsersOld"
dlag <- 2
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

# Library

#### Spain, Organic Search, UsersOld, corr: 0.653

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_bibliotecas_chn_es[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "UsersOld"
dlag <- 2
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### Locals, Organic Search, Users, corr: 0.622

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_bibliotecas_chn_lo[Channel == "Organic Search" & Date >= teststart & Date <= testend]
metric <- "Users"
dlag <- 0
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```

#### Spain, Direct, Users, corr: 0.592

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2016-08-04"  # Values for Full Data
testend <- "2018-05-24"
visitordata <- fjm_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
gadata <- ga_bibliotecas_chn_es[Channel == "Direct" & Date >= teststart & Date <= testend]
metric <- "Users"
dlag <- 2
plotLagComparison(trendValues(gadata),
                  trendValues(visitordata),
                  metric = metric,
                  dlag = dlag)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(trendValues(gadata),
                           trendValues(visitordata),
                           metric = metric,
                           dlag = dlag)
```